```{r setup-robust, echo = FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
temp_eval <- FALSE
```

# Checking for Robustness {#robust}

Once you have assessed and improved the computational reproducibility of a paper, you can assess the quality of different analytical choices by conducting new **robustness checks**, or changes in computational choices, both in data analysis and data cleaning, and reporting their subsequent effects on the estimates of interest. The universe of robustness checks can be very large (potentially infinite!). Your focus should be on the set of **reasonable specifications** ([Simonsohn et. al., 2018](https://urisohn.com/sohn_files/wp/wordpress/wp-content/uploads/Paper-Specification-curve-2018-11-02.pdf)), defined as (i) sensible tests of the research question, (ii) expected to be statistically valid, and (iii) not redundant with other specifications in the set.

The addition of new robustness checks will depend on the paper's current level of reproducibility. For example, it won't be possible to perform additional robustness checks for claims supported by display items reproducible at levels 0-1 because there is no data to work with. It may be possible to perform additional robustness checks for claims supported by display items reproducible at levels 2-4, but not using the specific estimates declared in the *Scoping Stage* since the display items are not computationally reproducible from analysis data (CRA). It is possible to conduct additional robustness checks to validate core conclusions of a claim based on a display item reproducible at level 5. Finally, claims associated with display items reproducible at level 6 or higher allow for robustness checks that involve variable definitions and data manipulations. 

The size of reasonable robustness checks grows exponentialy as higher levels of computational reproducibility are achieved. For example, when checking the robustness to a new variable definition, you will also be able to test the combination of how the main estimate changes under an alternative variable definition *and* an alternative core analytical choice.

Robustness begins at the claim level (see our diagram representing a paper's components (\@ref(fig:stages-unit))). For a given claim, there will be several specifications presented, one of which will be identified by the authors (or yourself if the authors do not identify one) as the main or preferred specification. Identify which display item contains this specification and refer to the reproduction tree to identify the code files in which you can modify a computational choice. Using the [example tree](#complete-tree) discussed in the *Assessment* stage, we can obtain the following, removing the data files for simplicity. This simplified tree provides a list of potential files in which you can test different reasonable specifications: 

        table1.tex (contains preferred specification of a given claim)
            |___[code] analysis.R
                    |___[code] final_merge.do
                            |___[code] clean_merged_1_2.do
                            |       |___[code] merge_1_2.do
                            |               |___[code] clean_raw_1.py
                            |               |___[code] clean_raw_2.py
                            |___[code] clean_merged_3_4.do
                                    |___[code] merge_3_4.do
                                            |___[code] clean_raw_3.py
                                            |___[code] clean_raw_4.py
                                            
Here we suggest two types of contributions to robustness checks: (1) mapping the universe of robustness checks and (2) testing reasonable specifications. Both contributions should be recorded on the ACRE platform referring to files in a specific reproduction package. 

## Mapping the universe of robustness checks

**Analytical choices in data cleaning code**

  - Variable definition
  - Data sub-setting
  - Data reshaping (merge, append, long/gather, wide/spread)
  - Others (specify as "processing - other")
  
**Analytical choices in analysis code** 

   - Regression function (link function)
   - Key parameters (tuning, tolerance parameters, etc.)
   - Controls
   - Adjustment of standard errors
   - Choice of weights
   - Treatment of missing values
   - Imputations
   - Other (specify as "methods - other")

Once finished, transcribe all of the information on analytical choices into a dataset. For the `source` field, type *“original”* whenever the analytical choice is identified for the first time, and `file_name-line number` each time the same analytical choice is applied thereafter (for example, if an analytic choice is identified for the first time in line #103 and for the second time in line #122 their respective values for the `source` field should be `original` and `code_01.do-L103`).

For each analytical choice recorded, add the specific choice used in the paper, and describe what alternatives could have been used. The resulting database should have the [following structure](https://docs.google.com/spreadsheets/d/1nZuJSHswbZgaaIfBcyIUGPwG-WIP8zE1Oambud-WoDc/edit?usp=sharing):

```{r robust-checks, echo = FALSE, eval=temp_eval}
robust_checks <- data.frame(entry_id = c("1", "2", "3", "..."),
                            file_name = c("code_01.do", "code_01.do", "code_05.R", "..."),
                            line_number = c("73", "122", "143", "..."),
                            choice_type = c("data sub-setting", "variable definition", "controls", "..."),
                            choice_value = c("males", "income = wages + capital gains", "age, income, education", "..."),
                            choice_range = c("males, female", "wages, capital gains, gifts", "age, income, education, region", "..."),
                            source = c("original", '"code_01.do-L103"', "original", "..."))
                         
robust_checks %>%
    knitr::kable() %>%
    kable_styling(full_width = TRUE) %>%
    scroll_box(width = "100%", box_css = "border: 0px;")
```

|entry_id| file_name  | line_number | choice_type         | choice_value                   | choice_range                  | Source              |
|--------|------------|-------------|---------------------|--------------------------------|-------------------------------|---------------------|
|   1    | code_01.do | 73          | data sub-setting    | males                          | males, female,                | original            |
|   2    | code_01.do | 122         | variable definition | income = wages + capital gains | wages, capital gains, gifts   | "code_01.do-L103"   |
|   3    | code_05.R  | 143         | controls            | age, income, education         | age, income, education, region| original            |
| ...    | ...        | ...         | ...                 | ...                            | ...                           | ...                 |

An advantage of this type of contribution is that you need not have an in-depth knowledge of the paper and its methodology to contribute. This allows you to potentially map several code files, achieving a broader understanding of the paper. The disadvantage is that you are not expected to test alternative specifications. 

## Proposing a specific robustness check

When performing a specific robustness test, follow these steps: 

1. Search the mapping database (discussed above) and record the identifier(s) corresponding to the analytical choice to test (`entry_id`). If there is no entry corresponding for the specific lines, create one yourself. 

2. Propose a specific variation to this analytical choice. 

3. Discuss whether you think this variation is sensible, specifically in the context of the claim tested (e.g., does it make sense to include or exclude low-income Hispanic people from the sample?). 

4. Discuss how this variation could affect the validity of the results (e.g., likely effects on omitted variable bias, measurement error, change in the Local Average Treatment Effects for the underlying population). 

5. Confirm that test is not redundant with other tests in the paper or robustness exercise. 

6. Report the results from the robustness check (new estimate, standard error, and units).


The advantage of this approach is that it allows for an in-depth inspection of a specific section of the paper. The main limitation is that justifying sensibility and validity (and non-redundancy, to an extent) requires a deeper understanding of the paper's topic and the methods, making it less feasible for undergraduate students or graduates with only a surface-level interest in the paper. 

<!--
## Test the robustness of results  

Test the robustness of results to alternative (sensible) specifications

  - Specification curves: DESCRIBE. 
  - Jackknife the preferred estimate: DESCRIBE.  
  - Use ML to select among excoriates: DESCRIBE.    
-->
 


