```{r setup-more-diagrams, echo = FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
temp_eval <- TRUE
```

# Examples of Reproduction Trees 
A diagram generated by the [Diagram Builder](#diagram) which represents all the available data and code on behind a specific display item. The tree is meant to represent the entire computational workflow behind a result from the paper. It allows reproducers to trace a display item to its primary sources. It can also be used to guide users of the reproduction package and/or to identify missing components for a complete reproduction. 

A reproduction tree is complete when it is possible to connect its output (a given display item) with all of its inputs down to the raw data. A reproduction is incomplete when it is not possible to connect all the inputs to the resulting display item. Paraphrasing the author Leo Tolstoy, *complete workflows are all alike; every incomplete computational workflow is incomplete in its own way*. This chapter presents a few examples of reproduction trees, focusing particularly on the many possible ways in which a tree could be incomplete. If you have a reproduction tree that contains an instructive example please [contribute](#contrib-guide) to this chapter (via a pull request or emailing your reproduction tree to [ACRE@berkeley.edu](mailto:ACRE@berkeley.edu).) 


## Stylized examples

### Complete reproduction tree
Below is an example of output from the [Diagram Builder](#diagram) for a display item that can be fully constructed using the files contained in the reproduction package. The diagram displays files as outputs and inputs to code scripts all the way down to the raw data.

```
          table 1
            └───[code] formatting_table1.R
                ├───output1_part1.txt  
                |   └───[code] output_table1.do           
                |       └───[data] analysis_data01.csv
                |          └───[code] data_cleaning01.R
                |             └───[data] survey_01raw.csv
                └───output1_part2.txt  
                    └───[code] output_table2.do           
                        └───[data] analysis_data02.csv
                           └───[code] data_cleaning02.R
                              └───[data] admin_01raw.csv  
```

### Incomplete reproduction tree

#### Raw data and analytic data are available, but cleaning code is missing.

Below is an example of output from the [Diagram Builder](#diagram) for a display item that is missing some of the code needed to generate it from the raw data. There are two reasons to suspect that this workflow is incomplete: (i) there is no clear data cleaning step (only analysis that generates output and formatting), and (ii) there are unused files that are likely to be raw data. None of these reasons can confirm unequivocally that the tree is incomplete, but a reproducer familiar with the paper and its data sources could use the tree to certify its (in)completeness and request missing files.  

```
          table 1
            └───[code] formatting_table1.R
                ├───output1_part1.txt  
                |   └───[code] output_table1.do           
                |       └───[data] analysis_data01.csv
                └───output1_part2.txt  
                    └───[code] output_table2.do           
                        └───[data] analysis_data02.csv

           Unused files: 
           - survey_01raw.csv
           - admin_01raw.csv  
```

Reproducers are asked to speculate on where the missing files might go, and hence propose how a complete tree might look like (where possible). For this example, we have assumed there are missing code scripts that at some point take in `survey_01raw.csv` and `admin_01raw.csv`, and eventually output `analysis_data01.csv` and `analysis_data02.csv`, though this requires the reproducer's discretion.

```
          table 1
            └───[code] formatting_table1.R
                ├───output1_part1.txt  
                |   └───[code] output_table1.do           
                |       └───[data] analysis_data01.csv
                |          └───[code] MISSING FILE(S)
                |             └───[data] survey_01raw.csv
                └───output1_part2.txt  
                    └───[code] output_table2.do           
                        └───[data] analysis_data02.csv
                           └───[code] MISSING FILE(S)
                              └───[data] admin_01raw.csv  
```

### Unused data sources

It is possible that not all data included in a replication package are actually used in code scripts in the reproduction package. This would be the case if, for example, the raw data and analysis data are included, but not the script that generates the analysis data. As a concrete example, consider what the original diagram above would look like if the only code included in the reproduction package were analysis.R:

```
        table1.tex
            |___[code] analysis.R
                |___analysis_data.dta

        Unused data sources:
        raw_1.dta
        raw_2.dta
        raw_3.dta
        raw_4.dta

        Unused analysis data:
        cleaned_1.dta
        cleaned_2.dta
        cleaned_3.dta
        cleaned_4.dta
        merged_1_2.dta
        merged_3_4.dta
        cleaned_1_2.dta
        cleaned_3_4.dta
```

In this case, there are many data files that were listed in the raw data and analytic data spreadsheets that are not used by any code script in the replication package.


### Final outputs is not a display item  

Below is a sample solution if the output file is missing while all needed code and data are available. In this case, a complete [Diagram Builder](#diagram) is still feasible with a placeholder for the missing output specifying the output (e.g., Fig 2 or Table 1) location displayed in the paper. 

```
        [Placeholder: Fig 1 Plot]
            |___replication.do
                |___state_BEA.dta
   
                
        [Placeholder: Fig 2 Plot]
            |___replication.do
                |___county_BEA.dta
     
```

## Examples from real reproduction attempts


### Possibly missing code for producing a display item^[This is from a reproduction attempt conducted as part of a UC Berkeley Development Economics course].

This reproduction diagram fragment likely shows a missing piece of code. In a complete reproduction package there are no unused files and all final outputs are display items. `cps2018.dta` and `cps_march2017.dta` are included as inputs in the reproduction kit, but never used to make a display item, i.e., there is no piece of code that is listed as using them as inputs. Likewise, `PublicSalary.dta` is listed as a final output, meaning it, too, is not used to make a display item since it is not listed as an input for any code script. Perhaps `Paper2_PoExitDataset.dta` is made by a missing code script that takes `PublicSalary.dta`, `cps2018.dta`, and `cps_march2017.dta` as inputs? It may be the case that the only way to find out for sure is to contact the study author(s), in which case, such a diagram can be used to help them identify any missing files.

```
        PublicSalary.dta
        |___MakeData2.do
            |___Paper2_ProviderDataset.dta
            |___Paper2_SSPDataset_wIRT_final.dta
            |___PublicFacilitySurvey_clean.dta

        Table1.xml
        |___Table1.do
            |___ProviderData.dta
            |   |___MakeData4.do
            |       |___Paper2_PoExitDataset.dta
            |       |___Paper2_ProviderDataset.dta
            |       |___Paper2_SSPDataset_wIRT_final.dta
            |___VillageDataset.dta
            |   |___MakeData8.do
            |       |___Paper2_HouseholdDataset1.dta
            |       |___Paper2_VillageDataset.dta
            |___HouseholdDataset.dta
                |___MakeData8.do
                    |___Paper2_HouseholdDataset1.dta
                    |___Paper2_VillageDataset.dta

        Unusued data sources:
        cps2018.dta
        cps_march2017.dta  
```

### Long, complicated tree^[This is from a reproduction attempt conducted as part of a UC Berkeley Development Economics course].

This diagram shows that the production of a given display item may be very complicated, highlighting the usefulness of the [Diagram Builder](#diagram) as a visualization tool. In reproducing such a complicated display item, it can be useful to have such a diagram to determine, for example, the order in which code scripts should be run, what files might depend on a faulty code script, or which files are necessary to keep if the goal is to only produce the specific display item.


<!--
FIGURE OUT A WAY TO ONLY PRINT IN HTML OUTPUT
```{style="max-height: 300px;"}
        results_days.dta
        |___lightspaper_replication.do
            |___isocvout.dbf
            |   |___v4cvggini_bycountry_prep.aml
            |       |___ctryliggrid
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___l%sy%nm
            |       |   |___v4lightsprep.aml
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___gluareag_alpha1.asc
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tif
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___cvg%sy%
            |       |   |___v4lightsprep.aml
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___gluareag_alpha1.asc
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tif
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___isocvgst.dbf
            |       |   |___pre_aml.do
            |       |       |___afpv1.csv
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___ctrynum.dbf
            |       |___ginistrt.dbf
            |           |___pre_aml.do
            |               |___afpv1.csv
            |               |   |___v4unzip.bat
            |               |       |___rad_cal.tar
            |               |       |___phys_geo.zip
            |               |       |___world_avg_fixed.tfw
            |               |       |___af_grumpv1_ppoints_csv.zip
            |               |       |___gl_grumpv1_area_ascii_30.zip
            |               |       |___malaria_ecology.zip
            |               |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |               |       |___gasflares.zip
            |               |       |___F%sy%.v4.tar
            |               |       |___boundaries.zip
            |               |___ctrynum.dbf
            |___ginioutu.dbf
            |   |___v4cvggini_bycountry_prep.aml
            |       |___ctryliggrid
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___l%sy%nm
            |       |   |___v4lightsprep.aml
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___gluareag_alpha1.asc
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tif
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___cvg%sy%
            |       |   |___v4lightsprep.aml
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___gluareag_alpha1.asc
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___world_avg.tif
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___isocvgst.dbf
            |       |   |___pre_aml.do
            |       |       |___afpv1.csv
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___ctrynum.dbf
            |       |___ginistrt.dbf
            |           |___pre_aml.do
            |               |___afpv1.csv
            |               |   |___v4unzip.bat
            |               |       |___rad_cal.tar
            |               |       |___phys_geo.zip
            |               |       |___world_avg_fixed.tfw
            |               |       |___af_grumpv1_ppoints_csv.zip
            |               |       |___gl_grumpv1_area_ascii_30.zip
            |               |       |___malaria_ecology.zip
            |               |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |               |       |___gasflares.zip
            |               |       |___F%sy%.v4.tar
            |               |       |___boundaries.zip
            |               |___ctrynum.dbf
            |___global_total_dn_uncal_longdiff9206.dta
            |   |___v4lights_stataprep_uncal.do
            |       |___ctryoutu.dbf
            |       |   |___v4ctrytables_uncal.aml
            |       |       |___ctryliggrid
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___l%sy%nm
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___cvg%sy%
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___gluareag
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___ctrynum.dbf
            |       |       |___gasflares.shp
            |       |       |   |___merge_gf.pyw
            |       |       |       |___afprimates.csv
            |       |       |       |   |___pre_aml.do
            |       |       |       |       |___afpv1.csv
            |       |       |       |       |   |___v4unzip.bat
            |       |       |       |       |       |___rad_cal.tar
            |       |       |       |       |       |___phys_geo.zip
            |       |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |       |___gasflares.zip
            |       |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |       |___boundaries.zip
            |       |       |       |       |___ctrynum.dbf
            |       |       |       |___gas flares by country
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___glp00ag
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___dhselect.xls
            |       |___wb_dq.xls
            |       |___ctryout2.dbf
            |       |   |___v4ctrytables_uncal.aml
            |       |       |___ctryliggrid
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___l%sy%nm
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___cvg%sy%
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___gluareag
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___ctrynum.dbf
            |       |       |___gasflares.shp
            |       |       |   |___merge_gf.pyw
            |       |       |       |___afprimates.csv
            |       |       |       |   |___pre_aml.do
            |       |       |       |       |___afpv1.csv
            |       |       |       |       |   |___v4unzip.bat
            |       |       |       |       |       |___rad_cal.tar
            |       |       |       |       |       |___phys_geo.zip
            |       |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |       |___gasflares.zip
            |       |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |       |___boundaries.zip
            |       |       |       |       |___ctrynum.dbf
            |       |       |       |___gas flares by country
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___glp00ag
            |       |           |___v4unzip.bat
            |       |               |___rad_cal.tar
            |       |               |___phys_geo.zip
            |       |               |___world_avg_fixed.tfw
            |       |               |___af_grumpv1_ppoints_csv.zip
            |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |               |___malaria_ecology.zip
            |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |___gasflares.zip
            |       |               |___F%sy%.v4.tar
            |       |               |___boundaries.zip
            |       |___ginioutu.dbf
            |       |   |___v4cvggini_bycountry_prep.aml
            |       |       |___ctryliggrid
            |       |       |   |___v4unzip.bat
            |       |       |       |___rad_cal.tar
            |       |       |       |___phys_geo.zip
            |       |       |       |___world_avg_fixed.tfw
            |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |___malaria_ecology.zip
            |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |___gasflares.zip
            |       |       |       |___F%sy%.v4.tar
            |       |       |       |___boundaries.zip
            |       |       |___l%sy%nm
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___cvg%sy%
            |       |       |   |___v4lightsprep.aml
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___gluareag_alpha1.asc
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___world_avg.tif
            |       |       |           |___v4unzip.bat
            |       |       |               |___rad_cal.tar
            |       |       |               |___phys_geo.zip
            |       |       |               |___world_avg_fixed.tfw
            |       |       |               |___af_grumpv1_ppoints_csv.zip
            |       |       |               |___gl_grumpv1_area_ascii_30.zip
            |       |       |               |___malaria_ecology.zip
            |       |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |               |___gasflares.zip
            |       |       |               |___F%sy%.v4.tar
            |       |       |               |___boundaries.zip
            |       |       |___isocvgst.dbf
            |       |       |   |___pre_aml.do
            |       |       |       |___afpv1.csv
            |       |       |       |   |___v4unzip.bat
            |       |       |       |       |___rad_cal.tar
            |       |       |       |       |___phys_geo.zip
            |       |       |       |       |___world_avg_fixed.tfw
            |       |       |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |       |       |___malaria_ecology.zip
            |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |       |       |___gasflares.zip
            |       |       |       |       |___F%sy%.v4.tar
            |       |       |       |       |___boundaries.zip
            |       |       |       |___ctrynum.dbf
            |       |       |___ginistrt.dbf
            |       |           |___pre_aml.do
            |       |               |___afpv1.csv
            |       |               |   |___v4unzip.bat
            |       |               |       |___rad_cal.tar
            |       |               |       |___phys_geo.zip
            |       |               |       |___world_avg_fixed.tfw
            |       |               |       |___af_grumpv1_ppoints_csv.zip
            |       |               |       |___gl_grumpv1_area_ascii_30.zip
            |       |               |       |___malaria_ecology.zip
            |       |               |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |               |       |___gasflares.zip
            |       |               |       |___F%sy%.v4.tar
            |       |               |       |___boundaries.zip
            |       |               |___ctrynum.dbf
            |       |___wdi_limited.dta
            |       |___imf_dds.xls
            |       |___ginistata_uncal.dta
            |           |___v4ginicalc_uncal.do
            |               |___ginioutu.dbf
            |                   |___v4cvggini_bycountry_prep.aml
            |                       |___ctryliggrid
            |                       |   |___v4unzip.bat
            |                       |       |___rad_cal.tar
            |                       |       |___phys_geo.zip
            |                       |       |___world_avg_fixed.tfw
            |                       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |___malaria_ecology.zip
            |                       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |___gasflares.zip
            |                       |       |___F%sy%.v4.tar
            |                       |       |___boundaries.zip
            |                       |___l%sy%nm
            |                       |   |___v4lightsprep.aml
            |                       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___world_avg.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___gluareag_alpha1.asc
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.cf_cvg.tif
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___world_avg.tif
            |                       |           |___v4unzip.bat
            |                       |               |___rad_cal.tar
            |                       |               |___phys_geo.zip
            |                       |               |___world_avg_fixed.tfw
            |                       |               |___af_grumpv1_ppoints_csv.zip
            |                       |               |___gl_grumpv1_area_ascii_30.zip
            |                       |               |___malaria_ecology.zip
            |                       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |               |___gasflares.zip
            |                       |               |___F%sy%.v4.tar
            |                       |               |___boundaries.zip
            |                       |___cvg%sy%
            |                       |   |___v4lightsprep.aml
            |                       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___world_avg.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___gluareag_alpha1.asc
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.cf_cvg.tif
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___F%sy%.v4b_web.cf_cvg.tfw
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___world_avg.tif
            |                       |           |___v4unzip.bat
            |                       |               |___rad_cal.tar
            |                       |               |___phys_geo.zip
            |                       |               |___world_avg_fixed.tfw
            |                       |               |___af_grumpv1_ppoints_csv.zip
            |                       |               |___gl_grumpv1_area_ascii_30.zip
            |                       |               |___malaria_ecology.zip
            |                       |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |               |___gasflares.zip
            |                       |               |___F%sy%.v4.tar
            |                       |               |___boundaries.zip
            |                       |___isocvgst.dbf
            |                       |   |___pre_aml.do
            |                       |       |___afpv1.csv
            |                       |       |   |___v4unzip.bat
            |                       |       |       |___rad_cal.tar
            |                       |       |       |___phys_geo.zip
            |                       |       |       |___world_avg_fixed.tfw
            |                       |       |       |___af_grumpv1_ppoints_csv.zip
            |                       |       |       |___gl_grumpv1_area_ascii_30.zip
            |                       |       |       |___malaria_ecology.zip
            |                       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                       |       |       |___gasflares.zip
            |                       |       |       |___F%sy%.v4.tar
            |                       |       |       |___boundaries.zip
            |                       |       |___ctrynum.dbf
            |                       |___ginistrt.dbf
            |                           |___pre_aml.do
            |                               |___afpv1.csv
            |                               |   |___v4unzip.bat
            |                               |       |___rad_cal.tar
            |                               |       |___phys_geo.zip
            |                               |       |___world_avg_fixed.tfw
            |                               |       |___af_grumpv1_ppoints_csv.zip
            |                               |       |___gl_grumpv1_area_ascii_30.zip
            |                               |       |___malaria_ecology.zip
            |                               |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |                               |       |___gasflares.zip
            |                               |       |___F%sy%.v4.tar
            |                               |       |___boundaries.zip
            |                               |___ctrynum.dbf
            |___samptab.txt
            |   |___v4lightsprep.aml
            |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___world_avg.tfw
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___gluareag_alpha1.asc
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___F%sy%.v4b_web.cf_cvg.tif
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___F%sy%.v4b_web.cf_cvg.tfw
            |       |   |___v4unzip.bat
            |       |       |___rad_cal.tar
            |       |       |___phys_geo.zip
            |       |       |___world_avg_fixed.tfw
            |       |       |___af_grumpv1_ppoints_csv.zip
            |       |       |___gl_grumpv1_area_ascii_30.zip
            |       |       |___malaria_ecology.zip
            |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
            |       |       |___gasflares.zip
            |       |       |___F%sy%.v4.tar
            |       |       |___boundaries.zip
            |       |___world_avg.tif
            |           |___v4unzip.bat
            |               |___rad_cal.tar
            |               |___phys_geo.zip
            |               |___world_avg_fixed.tfw
            |               |___af_grumpv1_ppoints_csv.zip
            |               |___gl_grumpv1_area_ascii_30.zip
            |               |___malaria_ecology.zip
            |               |___gl_gpwv3_pcount_00_wrk_25.zip
            |               |___gasflares.zip
            |               |___F%sy%.v4.tar
            |               |___boundaries.zip
            |___global_total_dn_uncal.dta
                |___v4lights_stataprep_uncal.do
                    |___ctryoutu.dbf
                    |   |___v4ctrytables_uncal.aml
                    |       |___ctryliggrid
                    |       |   |___v4unzip.bat
                    |       |       |___rad_cal.tar
                    |       |       |___phys_geo.zip
                    |       |       |___world_avg_fixed.tfw
                    |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |___malaria_ecology.zip
                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |___gasflares.zip
                    |       |       |___F%sy%.v4.tar
                    |       |       |___boundaries.zip
                    |       |___l%sy%nm
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___cvg%sy%
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___gluareag
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___ctrynum.dbf
                    |       |___gasflares.shp
                    |       |   |___merge_gf.pyw
                    |       |       |___afprimates.csv
                    |       |       |   |___pre_aml.do
                    |       |       |       |___afpv1.csv
                    |       |       |       |   |___v4unzip.bat
                    |       |       |       |       |___rad_cal.tar
                    |       |       |       |       |___phys_geo.zip
                    |       |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |       |___malaria_ecology.zip
                    |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |       |___gasflares.zip
                    |       |       |       |       |___F%sy%.v4.tar
                    |       |       |       |       |___boundaries.zip
                    |       |       |       |___ctrynum.dbf
                    |       |       |___gas flares by country
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___glp00ag
                    |           |___v4unzip.bat
                    |               |___rad_cal.tar
                    |               |___phys_geo.zip
                    |               |___world_avg_fixed.tfw
                    |               |___af_grumpv1_ppoints_csv.zip
                    |               |___gl_grumpv1_area_ascii_30.zip
                    |               |___malaria_ecology.zip
                    |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |               |___gasflares.zip
                    |               |___F%sy%.v4.tar
                    |               |___boundaries.zip
                    |___dhselect.xls
                    |___wb_dq.xls
                    |___ctryout2.dbf
                    |   |___v4ctrytables_uncal.aml
                    |       |___ctryliggrid
                    |       |   |___v4unzip.bat
                    |       |       |___rad_cal.tar
                    |       |       |___phys_geo.zip
                    |       |       |___world_avg_fixed.tfw
                    |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |___malaria_ecology.zip
                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |___gasflares.zip
                    |       |       |___F%sy%.v4.tar
                    |       |       |___boundaries.zip
                    |       |___l%sy%nm
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___cvg%sy%
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___gluareag
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___ctrynum.dbf
                    |       |___gasflares.shp
                    |       |   |___merge_gf.pyw
                    |       |       |___afprimates.csv
                    |       |       |   |___pre_aml.do
                    |       |       |       |___afpv1.csv
                    |       |       |       |   |___v4unzip.bat
                    |       |       |       |       |___rad_cal.tar
                    |       |       |       |       |___phys_geo.zip
                    |       |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |       |___malaria_ecology.zip
                    |       |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |       |___gasflares.zip
                    |       |       |       |       |___F%sy%.v4.tar
                    |       |       |       |       |___boundaries.zip
                    |       |       |       |___ctrynum.dbf
                    |       |       |___gas flares by country
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___glp00ag
                    |           |___v4unzip.bat
                    |               |___rad_cal.tar
                    |               |___phys_geo.zip
                    |               |___world_avg_fixed.tfw
                    |               |___af_grumpv1_ppoints_csv.zip
                    |               |___gl_grumpv1_area_ascii_30.zip
                    |               |___malaria_ecology.zip
                    |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |               |___gasflares.zip
                    |               |___F%sy%.v4.tar
                    |               |___boundaries.zip
                    |___ginioutu.dbf
                    |   |___v4cvggini_bycountry_prep.aml
                    |       |___ctryliggrid
                    |       |   |___v4unzip.bat
                    |       |       |___rad_cal.tar
                    |       |       |___phys_geo.zip
                    |       |       |___world_avg_fixed.tfw
                    |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |___malaria_ecology.zip
                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |___gasflares.zip
                    |       |       |___F%sy%.v4.tar
                    |       |       |___boundaries.zip
                    |       |___l%sy%nm
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___cvg%sy%
                    |       |   |___v4lightsprep.aml
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___gluareag_alpha1.asc
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tif
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___F%sy%.v4b_web.cf_cvg.tfw
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___world_avg.tif
                    |       |           |___v4unzip.bat
                    |       |               |___rad_cal.tar
                    |       |               |___phys_geo.zip
                    |       |               |___world_avg_fixed.tfw
                    |       |               |___af_grumpv1_ppoints_csv.zip
                    |       |               |___gl_grumpv1_area_ascii_30.zip
                    |       |               |___malaria_ecology.zip
                    |       |               |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |               |___gasflares.zip
                    |       |               |___F%sy%.v4.tar
                    |       |               |___boundaries.zip
                    |       |___isocvgst.dbf
                    |       |   |___pre_aml.do
                    |       |       |___afpv1.csv
                    |       |       |   |___v4unzip.bat
                    |       |       |       |___rad_cal.tar
                    |       |       |       |___phys_geo.zip
                    |       |       |       |___world_avg_fixed.tfw
                    |       |       |       |___af_grumpv1_ppoints_csv.zip
                    |       |       |       |___gl_grumpv1_area_ascii_30.zip
                    |       |       |       |___malaria_ecology.zip
                    |       |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |       |       |       |___gasflares.zip
                    |       |       |       |___F%sy%.v4.tar
                    |       |       |       |___boundaries.zip
                    |       |       |___ctrynum.dbf
                    |       |___ginistrt.dbf
                    |           |___pre_aml.do
                    |               |___afpv1.csv
                    |               |   |___v4unzip.bat
                    |               |       |___rad_cal.tar
                    |               |       |___phys_geo.zip
                    |               |       |___world_avg_fixed.tfw
                    |               |       |___af_grumpv1_ppoints_csv.zip
                    |               |       |___gl_grumpv1_area_ascii_30.zip
                    |               |       |___malaria_ecology.zip
                    |               |       |___gl_gpwv3_pcount_00_wrk_25.zip
                    |               |       |___gasflares.zip
                    |               |       |___F%sy%.v4.tar
                    |               |       |___boundaries.zip
                    |               |___ctrynum.dbf
                    |___wdi_limited.dta
                    |___imf_dds.xls
                    |___ginistata_uncal.dta
                        |___v4ginicalc_uncal.do
                            |___ginioutu.dbf
                                |___v4cvggini_bycountry_prep.aml
                                    |___ctryliggrid
                                    |   |___v4unzip.bat
                                    |       |___rad_cal.tar
                                    |       |___phys_geo.zip
                                    |       |___world_avg_fixed.tfw
                                    |       |___af_grumpv1_ppoints_csv.zip
                                    |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |___malaria_ecology.zip
                                    |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |___gasflares.zip
                                    |       |___F%sy%.v4.tar
                                    |       |___boundaries.zip
                                    |___l%sy%nm
                                    |   |___v4lightsprep.aml
                                    |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___world_avg.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___gluareag_alpha1.asc
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.cf_cvg.tif
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.cf_cvg.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___world_avg.tif
                                    |           |___v4unzip.bat
                                    |               |___rad_cal.tar
                                    |               |___phys_geo.zip
                                    |               |___world_avg_fixed.tfw
                                    |               |___af_grumpv1_ppoints_csv.zip
                                    |               |___gl_grumpv1_area_ascii_30.zip
                                    |               |___malaria_ecology.zip
                                    |               |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |               |___gasflares.zip
                                    |               |___F%sy%.v4.tar
                                    |               |___boundaries.zip
                                    |___cvg%sy%
                                    |   |___v4lightsprep.aml
                                    |       |___F%sy%.v4b_web.stable_lights.avg_vis.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.stable_lights.avg_vis.tif
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___world_avg.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___gluareag_alpha1.asc
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.cf_cvg.tif
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___F%sy%.v4b_web.cf_cvg.tfw
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___world_avg.tif
                                    |           |___v4unzip.bat
                                    |               |___rad_cal.tar
                                    |               |___phys_geo.zip
                                    |               |___world_avg_fixed.tfw
                                    |               |___af_grumpv1_ppoints_csv.zip
                                    |               |___gl_grumpv1_area_ascii_30.zip
                                    |               |___malaria_ecology.zip
                                    |               |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |               |___gasflares.zip
                                    |               |___F%sy%.v4.tar
                                    |               |___boundaries.zip
                                    |___isocvgst.dbf
                                    |   |___pre_aml.do
                                    |       |___afpv1.csv
                                    |       |   |___v4unzip.bat
                                    |       |       |___rad_cal.tar
                                    |       |       |___phys_geo.zip
                                    |       |       |___world_avg_fixed.tfw
                                    |       |       |___af_grumpv1_ppoints_csv.zip
                                    |       |       |___gl_grumpv1_area_ascii_30.zip
                                    |       |       |___malaria_ecology.zip
                                    |       |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                    |       |       |___gasflares.zip
                                    |       |       |___F%sy%.v4.tar
                                    |       |       |___boundaries.zip
                                    |       |___ctrynum.dbf
                                    |___ginistrt.dbf
                                        |___pre_aml.do
                                            |___afpv1.csv
                                            |   |___v4unzip.bat
                                            |       |___rad_cal.tar
                                            |       |___phys_geo.zip
                                            |       |___world_avg_fixed.tfw
                                            |       |___af_grumpv1_ppoints_csv.zip
                                            |       |___gl_grumpv1_area_ascii_30.zip
                                            |       |___malaria_ecology.zip
                                            |       |___gl_gpwv3_pcount_00_wrk_25.zip
                                            |       |___gasflares.zip
                                            |       |___F%sy%.v4.tar
                                            |       |___boundaries.zip
                                            |___ctrynum.dbf

```

-->




### Example of completing reproduction tree

In many cases, some of the components of the workflow will not be easily identifiable (or missing) in the reproduction package. Here we present a more complex example that the one presented in the Asessement chaprer. The [Diagram Builder](#diagram) will return a partial reproduction tree diagram. For example, if the files `merge_1_2.do`, `merge_3_4.do`, and `final_merge.do` are missing from the previous diagram, the [Diagram Builder](#diagram) will produce the following diagram:

```
        cleaned_3.dta
            └──[code] clean_raw_3.py
                └──raw_3.dta

        table1.tex
            └──[code] analysis.R
                └──analysis_data.dta

        cleaned_3_4.dta
            └──[code] clean_merged_3_4.do
                └──merged_3_4.dta

        cleaned_1.dta
            └──[code] clean_raw_1.py
                └──raw_1.dta

        cleaned_2.dta
            └──[code] clean_raw_2.py
                └──raw_2.dta

        cleaned_4.dta
            └──[code] clean_raw_4.py
                └──raw_4.dta

        cleaned_1_2.dta
            └──[code] clean_merged_1_2.do
                └──merged_1_2.dta
        Unused data sources: None.
```

In this case, you can still manually combine this partial information with your knowledge from the paper and own judgement to produce a "candidate" tree diagram (which might lead to different reproducers recreating different diagrams). This may look like the following:

```
        table1.tex
            └──[code] analysis.R
                └──analysis_data.dta
                    └──MISSSING_CODE_FILE_3
                        └──cleaned_3_4.dta
                        |       └──[code] clean_merged_3_4.do
                        |           └──merged_3_4.dta
                        |               └──MISSSING_CODE_FILE_2
                        |                   └──cleaned_3.dta
                        |                   |       └──[code] clean_raw_3.py
                        |                   |           └──raw_3.dta    
                        |                   └──cleaned_4.dta
                        |                           └──[code] clean_raw_4.py
                        |                               └──raw_4.dta
                        └──cleaned_1_2.dta
                                └──[code] clean_merged_1_2.do
                                    └──merged_1_2.dta
                                        └──MISSSING_CODE_FILE_1
                                            └──cleaned_1.dta
                                            |       └──[code] clean_raw_1.py
                                            |           └──raw_1.dta
                                            |   
                                            └──cleaned_2.dta
                                                    └──[code] clean_raw_2.py
                                                        └──raw_2.dta
```

To leave a record of the reconstructed diagrams, you will have to amend the input spreadsheets using placeholders for the missing components. In the example above, you should add the following entries to the code description spreadsheet:
```{r adding-rows-extra, echo = FALSE}
adding_rows_to_code <- data.frame(file_name = c("...", "missing_file1", "missing_file2", "missing_file3"),
                                  location = c("...", "unknown", "unknown", "unknown"),
                                  inputs = c("...", "cleaned_1.dta, cleaned_2.dta", "cleaned_3.dta, cleaned_4.dta", "merged_3_4.dta, merged_1_2.dta"),
                                  outputs = c("...", "merged_1_2.dta", "merged_3_4.dta", "analysis_data.dta"),
                                  description = c("...", "missing code", "missing code", "missing code"),
                                  primary_type = c("...", "unknown", "unknown", "unknown"))

adding_rows_to_code %>%
    knitr::kable(caption = "Adding rows to code spreadsheet") %>%
    kable_styling(full_width = TRUE)
```

